---
title: "CFS_Analysis"
author: "Lina Weingartner"
date: "2023-05-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load_gh("paul-buerkner/brms","stan-dev/cmdstanr")
pacman::p_load(tidyverse, rethinking, conflicted, performance)
```

#scout for conflicts
```{r}
# conflict_scout()
 conflict_prefer("filter", "dplyr")
 conflict_prefer("ar", "brms")
conflict_prefer("extract", "rstan")
conflict_prefer("stan", "rstats")
conflict_prefer("lag", "dplyr")
conflict_prefer("extract", "rstan")
conflict_prefer("map", "purrr")
conflict_prefer("LOO", "brms")
conflict_prefer("rstudent", "rethinking")
conflict_prefer("stancode", "brms")
conflict_prefer("WAIC", "brms")
```

loading in the logfiles
```{r}
files =  list.files(path = "insert the filepath to your datafiles here", full.names = T)
data <-  files %>% map_df(~read_csv(.x, col_types = cols(.default = "?", Gender = "c", ID = "f", frameRate = "d", trial = "_", trials.thisRepN = "_", trials.thisTrialN = "_", expName = "_", key_resp_image.rt = "_", before_t = "_", stim_t = "_", total_t = "_", condition = "f")))

#check that they read in correctly
head(data)
```

create missing variables
```{r}
#index which type of stimulus was used
data <- data %>% 
  mutate(stimulus = as.factor(case_when(
                              grepl("scramble_face", filename) ~ "scrambled",
                              TRUE ~ "face")
          ))%>% 
#shorten important names
  rename(rt = RT_from_SO.rt, key_response = key_resp_image.keys, order = trials.thisN, index = trials.thisIndex) %>% 
#index which type of mondrian was used
  mutate(mondrian = ifelse((index %% 2) == 0, "round", "square"))
```

z-score transform response time and split data frame
```{r}
#remove potential NAs
data <- na.omit(data)
data <- data %>% 
  mutate(rt_cent = scale(rt))%>% 
  #filter(correct_response==1)
#save cleaned data
write.csv(data, "insert path you would like to save the file to")
data_cfs <- data %>% 
  filter(condition == "cfs")
data_nocfs <- data %>% 
  filter(condition == "nocfs")

```

demographics
```{r}
mean(data$Age)
sd(data$Age)
```

check modelling assumptions
```{r}
round(pastecs::stat.desc(cbind(data_cfs$rt), basic =
    FALSE, norm = TRUE), digits = 3)
data_cfs$rt %>% qqnorm (pch = 16, frame = FALSE)
data_cfs$rt %>% qqline (col = "firebrick", lwd = 3)
```
and for noCFS
```{r}
round(pastecs::stat.desc(cbind(data_nocfs$rt), basic =
    FALSE, norm = TRUE), digits = 3)
data_nocfs$rt %>% qqnorm (pch = 16, frame = FALSE)
data_nocfs$rt %>% qqline (col = "firebrick", lwd = 3)
```

compare mean  response time for cfs and nocfs
```{r}
data %>% 
  group_by(condition) %>% 
  summarise(mean = mean(rt, na.rm = T), sd = sd(rt, na.rm = T))
```

compare mean response times across a number of variables to see what to include in the model
```{r}
data_cfs %>% 
  group_by(stimulus) %>% 
  summarise(mean = mean(rt), sd = sd(rt))

data_cfs %>% 
  group_by(mondrian) %>% 
  summarise(mean = mean(rt), sd = sd(rt))

data_cfs %>% 
  group_by(position) %>% 
  summarise(mean = mean(rt), sd = sd(rt))

data_cfs %>% 
  group_by(Gender) %>% 
  summarise(mean = mean(rt), sd = sd(rt))

data_cfs %>% summarise(mean = mean(rt))

```
define model formula
```{r}
f_face <- bf(rt_cent ~ 1 + stimulus + Gender + (1 + stimulus|ID))
```

set the priors
```{r}
get_prior(f_face, data = data_cfs)

h_priors<- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 1), class = sd, coef = Intercept, group = ID),
  prior(normal(0, 0.3), class = b),
  prior(normal(0, 1), class = sd, coef = stimulusscrambled, group = ID),
  prior(normal(1, 0.5), class = sigma),
  prior(lkj(2), class = cor))
```

prior predictive check
```{r}
m_face_p <- brm(f_face, data = data_cfs, family = gaussian, prior = h_priors, sample_prior = "only")

pp_check(m_face_p)
```

fit model and posterior predictive check
```{r}
m_face <- brm(f_face, data = data_cfs, family = gaussian, prior = h_priors, sample_prior = T)

pp_check(m_face)
```

```{r}
summary(m_face)
```
```{r}
plot(conditional_effects(m_face), points=T)
```



same procedure for noCFS
```{r}
m_face_nocfs <- brm(f_face, data = data_nocfs, family = gaussian, prior = h_priors, sample_prior = "only")
```

```{r}
pp_check(m_face_nocfs)
```
```{r}
m_face_nocfs <- brm(f_face, data = data_nocfs, family = gaussian, prior = h_priors, sample_prior = T)
```
```{r}
pp_check(m_face_nocfs)

```
 

```{r}
summary(m_face_nocfs)
```

```{r}
plot(conditional_effects(m_face_nocfs), points=T)
```
